\begin{rubric}{Conferences}

\entry*[Talk] {TMS Annual Meeting \& Exhibition, San Diego, CA, USA (March 2026)
    \par Interface-Mediated Deformation Transition and Quantum Confinement Effects in Ta$_2$O$_5$/SiO$_2$ Optical Nanolaminates.
    \par Session: Interface-Driven Plasticity and Fracture in Nanostructured and Layered Materials.}

\entry*[Talk] {TMS Annual Meeting \& Exhibition, San Diego, CA, USA (March 2026)
    \par Hydrogen-Enhanced Localized Plasticity in Nanoparticle-Reinforced CoCrFeNi Medium-Entropy Alloys.
    \par Session: Alloy Synthesis and Processing.}

\entry*[Talk] {TMS Annual Meeting \& Exhibition, San Diego, CA, USA (March 2026)
    \par In-Situ TEM Investigation of Fracture Growth in Novel Nanolaminate Thin Films.
    \par Session: Advanced Characterization Techniques for Quantifying and Modeling Deformation - Electron Microscopy.}

\entry*[Talk] {EMPA Department 020 Kick-off Meeting (January 2026)
    \par In-Situ Nanomechanics and Electron Diffraction in TEM: Revealing Deformation Mechanisms in Nanolaminate Structures.}

\entry*[Talk] {In situ Electron Microscopy Workshop, Toulouse, France (January 2026)
    \par Advanced in situ TEM techniques for nanomaterial characterization.}

\entry*[Talk] {EMPA Board of Governors Department 206 Meeting (September 2025)
    \par Probing deformation mechanics at micro-/nanoscale.}

\entry*[Talk] {FEMS-Euromat, Granada, Spain (2025)
    \par Hydrogen induced softening and deformation mechanisms in nanoparticle reinforced CoCrFeNi.}

\entry*[Talk] {FEMS-Euromat, Granada, Spain (2025)
    %\par Devulapalli, V., Vermeij, T., , Sharma, A., Michler, J., Maeder X.
    \par In situ TEM investigation of fracture growth in novel nanolaminate thin films.}

\entry*[Talk] {MecaNano - General meeting, Krakow, Poland (2025)
    %\par Devulapalli, V., Vermeij, T., , Sharma, A., Michler, J., Maeder X.
    \par Fracture behaviour in Cu-Al multilayer thin films with amorphous AlO interlayers: Insights from in-situ TEM tensile testing.}

\entry*[Talk] {International Conference on Correlative Electron Microscopy, Brno, Czech Republic (2025)
    %\par  Devulapalli, V., Vermeij, T., , Sharma, A., Michler, J., Maeder X.
    \par Enhancing Thin Film Toughness: The Role of Amorphous Interlayers.}

\entry*[Talk] {FEMS - Euromat, Frankfurt, Germany (2023)
    %\par Devulapalli, V., Schulz, F., Barreto, E., Ellendt, N., Jaegle, E., Dehm, G.
    \par Additively manufactured particle reinforced-CoCrFeNi: Microstructure, mechanical behaviour and hydrogen response.}

\entry*[Talk] {MSE Darmdtadt (Virtual), Darmstadt, Germany (2020)
    %\par Devulapalli, V., Dehm, G., Liebscher, C.
    \par Unravelling grain boundary structures in Ti thin films using aberration-corrected transmission electron microscopy.}

\entry*[Poster] {International Microscopy Conference (IMC20), South-Korea (2023)
    %\par Devulapalli, V., Frolov, T., Brink, T., Liebscher, C.
    \par Experimental observation of segregation induced grain boundary phase transition in titanium}
    
\entry*[Poster] {Microscopy Conference 2021, Vienna, Austria (Virtual) (2021)
    %\par Devulapalli, V., Hans, M., Prithiv, T. S., Schneider, J. M., Dehm, G., Liebscher, C. 
    \par Unravelling the atomic structure and segregation of $\Sigma$13 [0001] tilt grain boundaries in titanium by advanced STEM.}

%\entry*[Poster] {PICO 2021 (Virtual) (2021)
%    %\par Devulapalli, V., Hans, M., Schneider, J. M., Dehm, G., Liebscher, C.
%    \par Atomic structure and Fe-segregation in $\Sigma$13 [0001] Titanium tilt grain boundaries.}  


\entry*[Poster] {IAMNano, Düsseldorf, Germany (2019)
    %\par Devulapalli, V., Frommeyer, L., Ghidelli, M., Liebscher, C., Dehm, G. 
    \par From epitaxially grown thin films to grain boundary analysis in Cu and Ti.}

\end{rubric}


%\begin{rubric}{Conferences}
%
%\entry*[Poster] {International Microscopy Conference (IMC20), South-Korea (2023)
%    \par Devulapalli, V., Frolov, T., Brink, T., Liebscher, C.
%    \par Experimental observation of segregation induced grain boundary phase transition in titanium}
%    
%\entry*[Talk] {FEMS - Euromat, Frankfurt, Germany (2023)
%    \par Devulapalli, V., Schulz, F., Barreto, E., Ellendt, N., Jaegle, E., Dehm, G.
%    \par Additively manufactured particle reinforced-CoCrFeNi: Microstructure, mechanical behaviour and hydrogen response.}
%
%\entry*[Poster] {Microscopy Conference 2021, Vienna, Austria (Virtual) (2021)
%    \par Devulapalli, V., Hans, M., Prithiv, T. S., Schneider, J. M., Dehm, G., Liebscher, C. 
%    \par Unravelling the atomic structure and segregation of $\Sigma$13 [0001] tilt grain boundaries in titanium by advanced STEM.}
%
%\entry*[Poster] {PICO 2021 (Virtual) (2021)
%    \par Devulapalli, V., Hans, M., Schneider, J. M., Dehm, G., Liebscher, C.
%    \par Atomic structure and Fe-segregation in $\Sigma$13 [0001] Titanium tilt grain boundaries.}  
%
%\entry*[Talk] {MSE Darmdtadt (Virtual), Darmstadt, Germany (2020)
%    \par Devulapalli, V., Dehm, G., Liebscher, C.
%    \par Unravelling grain boundary structures in Ti thin films using aberration-corrected transmission electron microscopy.}
%
%\entry*[Poster] {IAMNano, Düsseldorf, Germany (2019)
%    \par Devulapalli, V., Frommeyer, L., Ghidelli, M., Liebscher, C., Dehm, G. 
%    \par From epitaxially grown thin films to grain boundary analysis in Cu and Ti.}
%
%\end{rubric}


